\documentclass[12pt]{article}

%
% From thesis.tex 
%
\usepackage{amsmath,amsthm,amsfonts,amscd}  % Some packages to write mathematics.
\usepackage{bbm}                   % math fone
\usepackage{eucal} 	 	% Euler fonts
\usepackage{graphicx}            % Newer package for eps figures
\usepackage[export]{adjustbox}
\usepackage{float}
\usepackage[hyphens]{url}		% Allows good typesetting of web URLs.
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}


%
% From jfesample.tex
%
\usepackage{setspace,enumitem}
\usepackage[longnamesfirst]{natbib}

\usepackage[margin=1in]{geometry}%

% Command to start a new page, starting on odd-numbered page if twoside option 
% is selected above
\newcommand{\clearRHS}{\clearpage\thispagestyle{empty}\cleardoublepage\thispagestyle{plain}}

% Number paragraphs and subparagraphs and include them in TOC
\setcounter{tocdepth}{2}

\usepackage{indentfirst} % Indent first sentence of a new section.
\usepackage{jfe}          % JFE-specific formatting of sections, etc.

\newtheorem{theorem}{Theorem}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{proposition}{Proposition}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}
\newtheorem{condition}{Condition}


%
% My commands
%

%\newcommand{\todo}[1]{\emph{TODO: #1}}
\newcommand{\todo}[1]{}

\DeclareMathOperator{\sign}{sign}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\Var}{\mathrm{Var}}
\DeclareMathOperator{\ind}{\mathbbm{1}}


\begin{document}

\setlist{noitemsep}  % Reduce space between list items (itemize, enumerate, etc.)

\title{Covered Interest Parity and Long-Term Bonds\footnotetext{This paper is an extension of my Masters thesis, of the same name.}}

\author{Michael Nahas \\ University of Texas at Austin}

\date{Compiled \today}

% Create title page with no page number

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\singlespacing

\maketitle

\vspace{-.2in}
\begin{abstract}
\noindent First, the major result of Liao (2016) was reproduced, with 3 additional currencies and 6 more years of data.  [Gordon Y. Liao. Credit Migration and Covered Interest Rate Parity. Working Paper 468601, Harvard University, October 2016.]   Second, Liao's model was tested using government rates, which showed a better fit than when using swap rates, as in Liao's work.  Lastly, CIP deviations were calculated from long-term corporate bond rates.  Since 2012, the CIP deviations measured using corporate bonds are lower than those calculated from swap and government rates, and are of a scale where banks could be expected to make arbitrage trades.  
\end{abstract}

\medskip

\noindent \textit{JEL classification}: G0.

\medskip
\noindent \textit{Keywords}: Covered interest parity; corporate bonds.

\thispagestyle{empty}

\clearpage

\onehalfspacing
\setcounter{footnote}{0}
\renewcommand{\thefootnote}{\arabic{footnote}}
\setcounter{page}{1}

\include{content}

\clearpage


\appendix

\include{appendix1}

\clearpage 

\include{appendix2}


\clearpage 

% Bibliography.

\bibliographystyle{jfe}
\bibliography{../currency_bibliography,../dataset_bibliography}

\end{document}
